Quality Criteria for SKOS Vocabularies

### 2012-03-20 introduction.tex

% What is SKOS?
The Simple Knowledge Organization System (SKOS)~\cite{Miles2005} is a standard model for sharing and linking controlled vocabularies on the Web. Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} have created SKOS representations of their controlled vocabularies and published them on the Web so that they can easily be accessed and by humans and machines.

@@

	\item The SKOS representation of Agrovoc defines concepts in 25 different languages. However, while most concepts have an English description, only 38\% of all concepts have German labels attached. This can be a problem for applications that use Agrovoc and rely on German translations.

@@

	\item The vocabulary developed by the Austrian Armed Forces (LVAk thesaurus\footnote{Non-public thesaurus developed by the Austrian Armed Forces}) contains 11 disconnected concept clusters. When we confronted the thesaurus maintainers with these structures, they recognized them as ``forgotten'' test data that has no practical significance.

@@

The goal of our work to help taxonomists in judging the quality of SKOS vocabularies, by giving them a set of computable quality criteria that can identify possible quality issues and serve as quantitative indicator for the quality of a given SKOS vocabulary. In combination with the taxonomists' experience and domain expertise, these criteria provide important feedback to the overall vocabulary design process. The main contributions of this work can be summarized as follows:

@@

	\item We identified existing \textbf{quality criteria} for controlled vocabularies by examining existing guidelines and formalized them into computable \textbf{filtering functions} that identify possibly affected resources in a given SKOS vocabulary.

@@

The results from our analysis show that... \todo{BH,CM}{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}

>>>>

% What is SKOS?
The Simple Knowledge Organization System (SKOS)~\cite{Miles2005} is a standard model for sharing and linking controlled vocabularies on the Web. Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} published SKOS representations of their controlled vocabularies on the Web so that they can easily be accessed and by humans and machines.

@@

	\item The SKOS representation of AGROVOC defines concepts in 25 different languages. However, while most concepts have an English description, only 38\% of all concepts have German labels attached. This can be a problem for applications that use Agrovoc and rely on German translations.

@@

	\item The non-public vocabulary developed by the Austrian Armed Forces (LVAk) contains 11 disconnected concept clusters. When we confronted the thesaurus maintainers with these structures, they recognized them as ``forgotten'' test data that has no practical significance.

@@

The goal of our work is to help taxonomists in judging the quality of SKOS vocabularies, by giving them a set of computable quality criteria that can identify possible quality issues and serve as quantitative indicator for the quality of a given SKOS vocabulary. In combination with the taxonomists' experience and domain expertise, these criteria provide important feedback to the overall vocabulary design process. The main contributions of this work can be summarized as follows:

@@

	\item We identified \todo{CM}{XX} \textbf{quality criteria} for SKOS vocabularies by examining existing guidelines and formalized them into computable \textbf{filtering functions} that identify possibly affected resources in a given SKOS vocabulary.

@@

In the following, we will first (Section~\ref{sec:background}) elaborate on the meaning of quality in SKOS vocabularies and then present the set of quality criteria we identified (Section~\ref{sec:criteria}). In Section~\ref{sec:analysis} we describe our analysis and discuss the results, which show that \todo{BH,CM}{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.}.
